---
title: "EDRM 718 Assignment #10"
author: "Anna Ehrhorn"
date: "April 17, 2020"
output: html_notebook
---

*This assignment will focus on importing and wrangling data.*


***
#### Question 1

Import and initial tidying of the *Johnson Elementary Project Data*.

```{r}
library(here)
library(tidyverse)

johnson.elem.data <- read_csv(here("Data", 
                                   "Johnson Elementary ELA Project.csv"), 
                              skip = 4, 
                              col_names = c("Room", "ID", "Tardies;Absences",
                                            "Q1", "Q2", "Q3", "Q4"))
                      
johnson.elem.data
```


Further tidying of the *Johnson Elementary Project Data*.

```{r}
tidy.JElem.data <- johnson.elem.data %>% 
  fill(Room) %>%
  drop_na(Room:Q4) %>%
  separate('Tardies;Absences', 
           into = c("Tardies", "Absences"), sep = ";",
           convert = TRUE) %>%
  col_factor(Room)

tidy.JElem.data
```



***
#### Question 2

Summary Statistics for the Number of Tardies and Abseneces for each Classroom.

```{r}
summary.tard.abs <- tidy.JElem.data %>%
  group_by(Room) %>%
  summarise(Tardies_mean = mean(Tardies),
            Tardies_sd = sd(Tardies),
            Absences_mean = mean(Absences),
            Absences_sd = sd(Absences))

summary.tard.abs
```


***
#### Question 3

The frequency of missing data points for each quarter (Q1, Q2, Q3, Q4) by 
Classroom. 

```{r}
missing.data <- tidy.JElem.data %>%
  group_by(Room) %>%
  replace(is.na(.), NA) %>%
  summarise_at(funs(sum(Q1:Q4)))

missing.data
```


***
#### Question 4

A graph that illustrates the median rating trends across the four quarters for
the fifth-grade classes.

```{r}
median.ratings.boxplot <- tidy.JElem.data %>%
  #make column of FOUR quarters together
  ggplot(aes(x = Room, y = )
```


***
#### Question 5


