---
title: "EDRM 718 Assignment #10"
author: "Anna Ehrhorn"
date: "April 17, 2020"
output: html_notebook
---

*This assignment will focus on importing and wrangling data.*


***
#### Question 1

Import and initial tidying of the *Johnson Elementary Project Data*.

```{r}
library(here)
library(tidyverse)

johnson.elem.data <- read_csv(here("Data", 
                                   "Johnson Elementary ELA Project.csv"), 
                              skip = 4, 
                              col_names = c("Room", "ID", "Tardies;Absences",
                                            "Q1", "Q2", "Q3", "Q4"),
                              col_types = cols(Room = col_factor(),
                                               ID = col_double(),
                                               'Tardies;Absences' = 
                                                 col_character(),
                                               Q1 = col_double(),
                                               Q2 = col_double(),
                                               Q3 = col_double(),
                                               Q4 = col_double()))
                      
johnson.elem.data
```


Further tidying of the *Johnson Elementary Project Data*.

```{r}
tidy.JElem.data <- johnson.elem.data %>% 
  fill(Room) %>%
  drop_na(ID) %>%
  separate('Tardies;Absences', 
           into = c("Tardies", "Absences"), sep = ";",
           convert = TRUE) %>%
  gather(Q1:Q4, key = "Quarter", value = "Rating")

tidy.JElem.data
```



***
#### Question 2

Summary Statistics for the Number of Tardies and Abseneces for each Classroom.

```{r}
summary.tard.abs <- tidy.JElem.data %>%
  group_by(Room) %>%
  summarize(Tardies_mean = mean(Tardies),
            Tardies_sd = sd(Tardies),
            Absences_mean = mean(Absences),
            Absences_sd = sd(Absences))

summary.tard.abs
```


***
#### Question 3

The frequency of missing data points for each quarter (Q1, Q2, Q3, Q4) by 
Classroom. 

```{r}
missing.JElem.class <- tidy.JElem.data %>%
  group_by(Room, Quarter) %>%
  summarize(sum(is.na(Rating)))

missing.JElem.class
```


***
#### Question 4

A graph that illustrates the median rating trends across the four quarters for
the fifth-grade classes.

```{r}
median.ratings.boxplot <- tidy.JElem.data %>%
  group_by(Room) %>%
  mutate(median_qscores = median(Rating)) %>% 
  ggplot(aes(x = Room, y = median_qscores)) +
    geom_boxplot() +
    labs(x = "Fifth Grade Classroom", y = "Median ELA Ratings", 
         title = "Fifth Grade ELA Ratings across Four Quarters for each Classroom")

median.ratings.boxplot
    
```


***
#### Question 5

Import and tidying of NYC Flight data.

```{r}

flights.data <- read_csv(here("Data", "NYC Flights 2013.csv"),
                         col_types = cols(carrier = col_factor(),
                                          origin = col_factor(),
                                          dest = col_factor()))

flights.data

tidy.flights.data <- flights.data %>% 
  separate(time_hour, 
           into = c("date", "hour"), sep = " ",
           convert = TRUE) 
  #parse_date(date) %>% #NOT WORKING
  #parse_time(hour)  

tidy.flights.data
  
```


A graph that compares flight carriers in terms of the proportion of 2013 flights
that arrived on time when traveling from New York City to Altanta.

```{r}
tidy.flights.data %>%
  filter(origin == "JFK", dest == "ATL") %>%
  geom_col(data = tidy.flights.data, 
           mapping = aes(x = carrier, y = arr_delay[arr_delay <= 0])) +
    stat_prop()
```

