---
title: "EDRM 718 Assignment #10"
author: "Anna Ehrhorn"
date: "April 17, 2020"
output: html_notebook
---

*This assignment will focus on importing and wrangling data.*


***
#### Question 1

Import and initial tidying of the *Johnson Elementary Project Data*.

```{r}
library(here)
library(tidyverse)

johnson.elem.data <- read_csv(here("Data", 
                                   "Johnson Elementary ELA Project.csv"), 
                              skip = 4, 
                              col_names = c("Room", "ID", "Tardies;Absences",
                                            "Q1", "Q2", "Q3", "Q4"),
                              col_types = cols(Room = col_factor(),
                                               ID = col_double(),
                                               'Tardies;Absences' = 
                                                 col_character(),
                                               Q1 = col_double(),
                                               Q2 = col_double(),
                                               Q3 = col_double(),
                                               Q4 = col_double()))
                      
johnson.elem.data
```


Further tidying of the *Johnson Elementary Project Data*.

```{r}
tidy.JElem.data <- johnson.elem.data %>% 
  fill(Room) %>%
  drop_na(Room:Q4) %>%
  separate('Tardies;Absences', 
           into = c("Tardies", "Absences"), sep = ";",
           convert = TRUE)

tidy.JElem.data
```



***
#### Question 2

Summary Statistics for the Number of Tardies and Abseneces for each Classroom.

```{r}
summary.tard.abs <- tidy.JElem.data %>%
  group_by(Room) %>%
  summarize(Tardies_mean = mean(Tardies),
            Tardies_sd = sd(Tardies),
            Absences_mean = mean(Absences),
            Absences_sd = sd(Absences))

summary.tard.abs
```


***
#### Question 3

The frequency of missing data points for each quarter (Q1, Q2, Q3, Q4) by 
Classroom. 

```{r}
tidy.JElem.data %>%
  group_by(Room) %>%
  count(sum(is.na(Q1:Q4)))
```


***
#### Question 4

A graph that illustrates the median rating trends across the four quarters for
the fifth-grade classes.

```{r}
median.ratings.boxplot <- tidy.JElem.data %>%
  add_column("ELA Year Median", median(Q1:Q4))

ggplot(aes(x = Room, y = ELA Year Median))
    
```


***
#### Question 5


